### 2014-03-27 ApTranscriptome_TR.Rmd
Changed  function to use robust regression function  from library(robustbase). Currently broken

# Load libraries
library(R.utils)
library(ggplot2)
library(knitr)
library(knitcitations)
library(pander)
library(stringr)
library(data.table)
library(RCurl)
library(plyr)

@@

# identify responsive transcripts
RxNout <- RxNseq(f = TPM.dt.sub, model = model, threshold = 0.05)

>>>>

# Load libraries
library(robustbase)
library(R.utils)
library(ggplot2)
library(knitr)
library(knitcitations)
library(pander)
library(stringr)
library(data.table)
library(RCurl)
library(plyr)

@@

# identify responsive transcripts using robust regression
testdata <- TPM.dt.sub[23:44,]

RxNout <- RxNseq(f = testdata, model = model, threshold = 0.05)
